Augraphy: A Data Augmentation Library for Document Images

### 2023-04-30 paper.tex
Fixed over-hanging line that was too long for page width

\smallskip
\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
In practice, these model the pipeline phases discussed previously with lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

>>>>

\smallskip
\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- intended to be applied in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable (behaves like a function).
In practice, these model the pipeline phases discussed previously with lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} applied in each \texttt{AugmentationPipeline} phase, and in each case yield the image, transformed by some of the Augmentations in the sequence.
